Predicting tree failure likelihood for utility risk mitigation via artificial intelligence

### 2021-03-03 docs/manuscript/manuscript.tex
merges and updates

    \includegraphics[width=\textwidth,angle=-90]{improbable-example-2}
    \caption{Improbable}
  \end{subfigure}
  \caption{Examples of training images in each of the three tree risk categories considered in this study: Probable, Possible and Improbable. Two are shown in each case.}
  \label{fig:raw_images}
\end{figure}

>>>>

    \includegraphics[width=\textwidth,angle=-90]{improbable-example-2}
    \caption{Improbable}
  \end{subfigure}
  \caption{Examples of training images in each of the three tree risk categories considered in this study.
  Trees in the left columnwere categorized as improbable due to their lack of structural defects as well as good physiologicalhealth. Trees in the center column were categorized as possible due to weak branch unions anddieback of crown extremities. Trees in the right column were categorized as probable for extensivesections of dead wood in the upper photograph, and a standing dead tree in the lower photograph.Images are antialiased in this figure for greater clarity}
  \label{fig:raw_images}
\end{figure}
